Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-06-14 manuscript/manuscript.tex
formal propositions

%\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
%  the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}

We will assume that the time series $\{X_t\}$ is stationary and strongly mixing, 
and $1/l+l/n\rightarrow 0$. We aim to show that under suitable assumptions
\begin{enumerate}
    \item $T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|$ 
    for some Gaussian process $G_{\infty}(\cdot)$ and Gaussian random variable 
    $U$ defined below.
    \item $|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$ for any fixed $x,$ 
    where $X_{1:n}:=\{X_1,\dots,X_n\}$ and $T_n^*$ is the the statistic computed 
    based on the bootstrap sample $X_1^*,\dots,X_n^*$). 
    Following the arguments in the proof of the Glivenko-Cantelli Theorem, we 
    may further strengthen this result to allow uniform convergence over $x$: 
    in other words, $\sup_x|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$.
\end{enumerate}
Sketches of the proofs for these propositions are shown as supporting 
information.

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  %Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	%$\hat\theta^{(b)}_n$ of $\theta$.
	Obtain parametrically fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	\eds{changed this to remove $F_\theta$, please check}\mc{looks good}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.

>>>>

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  %Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	%$\hat\theta^{(b)}_n$ of $\theta$.
	Obtain parametrically fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	\eds{changed this to remove $F_\theta$, please check}\mc{looks good}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}
The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.

\jy{Cite Kunsch (1989)}

\jy{In the supplement, use the proof environment to give proof
  sketches; make the title ``Supplement to `paper title` by
  authors''. No need to use their template for supp.}

Assume that the time series $\{X_t\}$ is stationary and
strongly mixing. The following results provides theoretical validity
of the NPBB procedure of the KS test. Sketches of their proofs are
in the Supplementary Information, with most arguments similar to those
in \citet{kunsch1989jackknife}.

\begin{proposition}\label{prop:Tn}
  As $1/l+l/n\rightarrow 0$,
  \[
    T_n \overset{d}{\rightarrow}
    \sup_x \big\vert G_{\infty}(x)+f(x;\theta_0)U \big\vert
  \]
  for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
  and Gaussian random variable  $U$.
\end{proposition}

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^*\leq x \mid \{X_t: t = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
  based on the bootstrap sample $\{X_t^*: t = 1, \ldots, n\}$.
\end{proposition}

Following the arguments in the proof of the Glivenko--Cantelli
Theorem, the result in Proposition~\ref{prop:Tnboot} can be further
strengthened to allow uniform convergence over $x$. That is,
\[
  \sup_x \big \vert
  \mathbb{P}(T_n^*\leq x|X_{1:n}) - \mathbb{P}(T_n\leq x) \big\vert
  \overset{a.s.}{\rightarrow} 0.
\]
